---
title: "Loan default prediction and Investment strategies"
date: "10/22/2021"
output: html_document
---


Importing libraries
```{r}
Pack <- c("tidyverse", "lubridate", "magrittr", "ggplotgui", "pROC", "dplyr", "ggplot2", "broom", "rpart", "C50", "ranger", "randomForest", "caret", "lift", "ROCR", "xgboost", "glmnet")
library(tidyverse)
library(lubridate)
library(magrittr)
library(ggplotgui)
library(pROC)
library(dplyr)
library(ranger)
library(ggplot2)
library(broom)
library(rpart)
library(C50)
library(randomForest)
library(caret)
library(lift)
library(ROCR)
library(glmnet)
library(xgboost)
```
What is the proportion of defaults (‘charged off’ vs ‘fully paid’ loans) in the data? 
```{r}
dfloans <- read.csv('lcData100K.csv')
  dfgrade<-dfloans %>% group_by(loan_status, grade,sub_grade) %>% tally()
  Dfcharged_off<-filter(dfloans,dfloans$loan_status=="Charged Off")
  dfgrade<-dfcharged_off %>% group_by(loan_status, grade,sub_grade) %>% tally()
```
The defaults are divided as follows: The share of Fully Paid loans is 97.5% and the share of Charged Off loans is 2.5%
```{r}
  tablepie<-sqldf("select loan_status, sum(count) as count from dataset5 group by loan_status")
  piepercent<- round(100*tablepie$count/sum(tablepie$count), 1)
  pie(piepercent, labels = piepercent, main = "Proportion of Fully Paid v/s Charged Off loans")
  legend("bottomright",legend=tablepie$loan_status,bty="n",fill=colors())
```
How does default rate vary with loan grade?
```{r}
p<-ggplot(data=table1, aes(x=grade, y=dfprop)) + geom_bar(stat="identity")
```
Does it vary with sub-grade?
```{r}
p<-ggplot(data=table1, aes(x=sub_grade, y=dfprop)) + geom_bar(stat="identity")
```
How many loans are there in each grade? 
```{r}
loan_amt<-dfloans %>% group_by(grade) %>% summarise(sum(loan_amnt))
  ggplot(data=dataset5, aes(x=grade, y=sum_loan_amnt)) + geom_bar(stat="identity")
```
do loan amounts vary by grade? 
```{r}
dataset5<-sqldf("Select purpose, count(loan_amnt),avg(loan_amnt),grade,loan_status from dfloans group by purpose")
ggplot(data=dataset5, aes(x=grade, y=mean_loan_amnt)) + geom_bar(stat="identity")
ggplot(data=dataset5, aes(x=grade, y=sum_loan_amnt)) + geom_bar(stat="identity")
```
Does interest rate for loans vary with grade, subgrade? 
```{r}
dataset2<- sqldf("Select grade, sub_grade ,avg(int_rate) as Mean_int_rate from dfloans group by grade, sub_grade order by grade, sub_grade")
ggplot(data=dataset2, aes(x=grade, y=Mean_int_rate)) + geom_bar(stat="identity")
ggplot(data=dataset2, aes(x=sub_grade, y=Mean_int_rate)) + geom_bar(stat="identity")
```
average, standard-deviation, min and max of interest rate by grade and subgrade
```{r}
avg_int_rate_by_grade<-dfloans %>% group_by(grade) %>% summarise(mean(int_rate))
avg_int_rate_by_subgrade<-dfloans %>% group_by(sub_grade) %>% summarise(mean(int_rate)) 
sd_by_grade<-dfloans %>% group_by(grade) %>% summarise(sd(int_rate))
sd_by_subgrade<-dfloans %>% group_by(sub_grade) %>% summarise(sd(int_rate))
min_by_grade<-dfloans %>% group_by(grade) %>% summarise(min(int_rate))
min_by_subgrade<-dfloans %>% group_by(sub_grade) %>% summarise(min(int_rate))
max_by_grade<-dfloans %>% group_by(grade) %>% summarise(max(int_rate))
max_by_subgrade<-dfloans %>% group_by(sub_grade) %>% summarise(max(int_rate))
```
For loans which are fully paid back, how does the time-to-full-payoff vary?
```{r}
convertdate<-dfloans$last_pymnt_d<-paste(dfloans$last_pymnt_d, "-01", sep = "")
converted_date<-dfloans$last_pymnt_d<-parse_date_time(dfloans$last_pymnt_d,  "myd")
actual_term<-as.duration(dfloans$issue_d  %--% dfloans$last_pymnt_d)
table_time_forpayoff<-data.frame(dfloans$grade,dfloans$loan_status,dfloans$issue_d,converted_date,actual_term)
tablefullypaid<-filter(table_time_forpayoff,dfloans.loan_status=="Fully Paid")
```
How does this actual-term vary by loan grade
```{r}
options(scipen=999)
boxplot(tablefullypaid$actual_term ~ tablefullypaid$dfloans.grade, data = tablefullypaid, xlab = " Grade",ylab = "Actual Term", main = "Actual Term v/s Grade")
```
Annual Return
```{r}
dfloans$actualTerm <- ifelse(dfloans$loan_status=="Fully Paid", as.duration(dfloans$issue_d  %--% dfloans$last_pymnt_d)/dyears(1), 3)
dfloans$actualReturn <- ifelse(dfloans$actualTerm>0, ((dfloans$total_pymnt -dfloans$funded_amnt)/dfloans$funded_amnt)*(1/dfloans$actualTerm)*100, 0)
dfloans %>% select(loan_status, int_rate, funded_amnt, total_pymnt, actualTerm, actualReturn) %>%  head()
tableReturns<-data.frame(dfloans$loan_status, dfloans$int_rate, dfloans$funded_amnt, dfloans$total_pymnt, dfloans$actualTerm, dfloans$actualReturn, dfloans$sub_grade, dfloans$grade,dfloans$int_rate)
tableReturnsclean<-na.omit(tableReturns)
```
Percentage Annual Return
```{r}
dfloans$actualReturn <- ifelse(dfloans$actualTerm>0, ((dfloans$total_pymnt -dfloans$funded_amnt)/dfloans$funded_amnt)*(1/dfloans$actualTerm)*100, 0)
```
Is there any return from loans which are ‘charged off’?
```{r}
dfloans$return_chargedOff <- ifelse(dfloans$loan_status=="Charged Off", as.duration(dfloans$issue_d  %--% dfloans$last_pymnt_d)/dyears(1), 3)
dfloans$actualReturn_chargedoff <- ifelse(dfloans$return_chargedOff >0, ((dfloans$total_pymnt -dfloans$funded_amnt)/dfloans$funded_amnt)*(1/dfloans$return_chargedOff )*100, 0)
tableReturns_chargedoff<-data.frame(dfloans$loan_status, dfloans$int_rate, dfloans$funded_amnt, dfloans$total_pymnt, dfloans$return_chargedOff, dfloans$actualReturn_chargedoff, dfloans$grade)
View(tableReturns_chargedoff)
tablereturns_chargedoff_clean<-na.omit(tableReturns_chargedoff)
View(tablereturns_chargedoff_clean)
```
How does return from charged - off loans vary by loan grade? 
```{r}
ggplot(data=tablereturns_chargedoff_clean, aes(x=dfloans.grade, y=dfloans.actualReturn_chargedoff)) + geom_bar(stat="identity")
```
Compare the average return values with the average interest_rate on loans
```{r}
qplot(dfloans.int_rate, dfloans.actualReturn, data = tablereturnspos, stat = 'summary', fun.y = 'mean')
```
How do returns vary by grade, and by sub-grade
```{r}
tablereturnspos<-filter(tableReturnsclean, dfloans.actualReturn>0)
ggplot(data=tablereturnspos, aes(x=dfloans.sub_grade, y=dfloans.actualReturn)) + geom_bar(stat="identity")
ggplot(data=tablereturnspos, aes(x=dfloans.grade, y=dfloans.actualReturn)) + geom_bar(stat="identity")
```
What are people borrowing money for (purpose)
```{r}
table5<-dfloans%>%group_by(purpose,grade)%>%tally()
table5b<-dfloans%>%group_by(purpose,grade)%>%summarise(mean(loan_amnt))
table5main<-data.frame(table5$purpose,table5$n,table5b$`mean(loan_amnt)`,dfloans$grade)
dataset5<-sqldf("Select purpose, count(loan_amnt),avg(loan_amnt),grade,loan_status from dfloans group by purpose")
```
Do loan amounts vary by purpose
```{r}
ggplot(data=dataset5, aes(x=sum_loan_amnt, y=purpose)) + geom_bar(stat="identity")
```
Do defaults vary by purpose?
```{r}
sqldf("select ((select sum_loan_amnt from dataset5 where loan_status = 'Charged Off')/(select sum_loan_amnt from dataset5))*100 as defaults, purpose from dataset5")
```
Does loan-grade assigned by Lending Club vary by purpose?
```{r}
ggplot(data=dataset5, aes(x=purpose, y=grade)) + geom_bar(stat="identity")
```
new derived attributes that may be useful for predicting default
```{r}
Dfcharged_off<-filter(dfloans,dfloans$loan_status=="Charged Off")
#1)
  default_rate<-round(100*Dfcharged_off$count/sum(dfloans$count), 1)
  #The default rate shows the percentage of defaulters out of the total loan borrowers.
  
  #2)
  unemployed_defaulters<-nrow(subset(dfloans, emp_length=="n/a" && loan_status=='Charged Off'))
  #The number of borrowers who are not employed and have not fully paid the loan can be used to predict whether a loan of a certain grade is likely to be charged off.
  
  #3)
  dfloans$annRet <- ((dfloans$total_pymnt -dfloans$funded_amnt)/dfloans$funded_amnt)*(12/36)*100
  #The annual returns help us look at the returns we are getting from certain loans yearly.
```
univariate analyses to determine which variables will be individually useful for predicting the dependent variable (loan_status)
```{r}
avg_credit_limit_by_grade<-dfloans %>% group_by(grade) %>% summarise(mean(tot_hi_cred_lim))
  
  avg_credit_limit_by_sub_grade<-dfloans %>% group_by(sub_grade) %>% summarise(mean(tot_hi_cred_lim))
  r<- (avg_credit_limit_by_grade[1])
  w<- (avg_credit_limit_by_grade[2])
  barplot(unlist(w),names.arg = c("A","B","C","D","E","F","G"), ylim=c(0,250000),xlab = "Grade", ylab = "Average Credit Limit")
  
  
 
  df<- (avg_credit_limit_by_sub_grade[1])
  dw<- (avg_credit_limit_by_sub_grade[2])
  barplot(unlist(dw),names.arg= c("Sub-Grade"),ylim=c(0,300000),xlab = "Sub-Grade", ylab = "Average Credit Limit")
  
  avg_credit_limit_by_loan_status<- dfloans %>% group_by(loan_status) %>% summarise(mean(tot_hi_cred_lim))
  dx<- (avg_credit_limit_by_loan_status[1])
  dt<- (avg_credit_limit_by_loan_status[2])
  barplot(unlist(dt),names.arg = c("Charged Off", "Fully Paid"),ylim=c(0,250000),xlab = "Loan Status", ylab = "Mean Credit Limit")
  
  avg_credit_limit_by_purpose<- dfloans %>% group_by(purpose) %>% summarise(mean(tot_hi_cred_lim))
  du<- (avg_credit_limit_by_purpose[1])
  dn<- (avg_credit_limit_by_purpose[2])
  barplot(unlist(dn),las=2,names.arg = c("Car","Credit_card","Debt consolidation", "Home improvement","House","Major Purchase","Medical", "Moving","Other","Renewable Energy","Small Business","Vacation", "Wedding"),ylim=c(0,250000),cex.names=0.5)
```

Loading the new curated dataset
```{r}
dtset <- read_csv("Downloads/dtset.csv")
glimpse(dtset)
view(dtset)
dtset <- dtset %>% select(-c("verification_status","num_accts_ever_120_pd","num_actv_rev_tl","tax_liens"))
dtset[sapply(dtset, is.character)] <- lapply(dtset[sapply(dtset, is.character)],as.factor)
sapply(dtset,class)
```
XGBoost 
```{r}
fdummy<-dummyVars(~.,data=dtset %>% select(-loan_status)) 
dxdf <- predict(fdummy, dtset)

levels(dtset$loan_status)   
dydf <- class2ind(dtset$loan_status, drop2nd = FALSE) 
#fpdf <- dydf [ , 2] 
codf <- dydf [ , 1]

dxdfTrn <- dxdf[trnIndex,]
codfTrn <- codf[trnIndex]
dxdfTst <- dxdf[-trnIndex,]
codfTst <- codf[-trnIndex]

dxTrn <- xgb.DMatrix( subset(dxdfTrn, select=-c(annRet, actualTerm, actualReturn, total_pymnt)), label=codfTrn)
dxTst <- xgb.DMatrix( subset(dxdfTst,select=-c(annRet, actualTerm, actualReturn, total_pymnt)), label=codfTst)

xgbWatchlist <- list(train = dxTrn, eval = dxTst)

xgbParam <- list (max_depth = 5, eta = 0.01, objective = "binary:logistic",eval_metric="error", eval_metric = "auc")

xgb_lsM1 <- xgb.train( xgbParam, dxTrn, nrounds = 500, xgbWatchlist, early_stopping_rounds = 10 )


xgb_lsM1$best_iteration # train-error:0.138071	train-auc:0.722638	eval-error:0.137100	eval-auc:0.692264 
 
xpredTrg<-predict(xgb_lsM1, dxTrn) # best_iteration is used
head(xpredTrg)

xgb_lsM1
 
table(pred=as.numeric(xpredTrg>0.5), act=codfTrn)

xpredTst<-predict(xgb_lsM1, dxTst)
pred_xgb_lsM1=prediction(xpredTst, dfTst$loan_status, label.ordering = c("Fully Paid","Charged Off"))
aucPerf_xgb_lsM1=performance(pred_xgb_lsM1, "tpr", "fpr")
plot(aucPerf_xgb_lsM1)
abline(a=0, b= 1)

xgbParam <- list (max_depth = 3, eta = 0.1, objective = "binary:logistic", eval_metric="error", eval_metric = "auc")

xgb_lscv <- xgb.cv( xgbParam, dxTrn, nrounds = 500, nfold=5, early_stopping_rounds = 10 )

xgb_lscv$best_iteration #train-error:0.137854+0.000317	train-auc:0.710371+0.000955	test-error:0.138214+0.001244	test-auc:0.685469+0.002394

best_cvIter <- which.max(xgb_lscv$evaluation_log$test_auc_mean)
xgb_lsbest <- xgb.train( xgbParam, dxTrn, nrounds = xgb_lscv$best_iteration )

xgb.importance(model = xgb_lsbest) %>% view()

xgbParam <- list (max_depth = 4, objective = "binary:logistic", eval_metric="error", eval_metric = "auc")
xgb_lsM1 <- xgb.train( xgbParam, dxTrn, nrounds = 500, xgbWatchlist, early_stopping_rounds = 10, eta=0.01 )

xgb_lsM1 <- xgb.train( xgbParam, dxTrn, nrounds = 500, xgbWatchlist, early_stopping_rounds = 10, eta=0.5 ) 
# Best iteration [19]:
#train-error:0.136971	train-auc:0.715195	eval-error:0.137867	eval-auc:0.689733

xgbParam1<-list(objective = "binary:logistic", eval_metric="auc", eval_metric = "error")

xgb_lsM1 <- xgb.train( xgbParam1, dxTrn, nrounds = 500, xgbWatchlist, 
early_stopping_rounds = 10, eta=0.1, max_depth=6 )
#Best iteration [9]:
#train-auc:0.708515	train-error:0.138143	eval-auc:0.683799	eval-error:0.137100

xgb_lsM1 <- xgb.train( xgbParam1, dxTrn, nrounds = 1000, xgbWatchlist, 
early_stopping_rounds = 10, eta=0.1, max_depth=6, lambda=0.05 )
#Best iteration [3]:
#	train-auc:0.700059	train-error:0.137900	eval-auc:0.680727	eval-error:0.137100

xgb_lsM1 <- xgb.train( xgbParam1, dxTrn, nrounds = 1000, xgbWatchlist, early_stopping_rounds = 10, eta=0.1, max_depth=6, lambda=0.05, subsample=0.7, colsample_bytree=0.5 )
#Best iteration [3]:
#	train-auc:0.691824	train-error:0.138157	eval-auc:0.678874	eval-error:0.137100

xgb_lsM1 <- xgb.train( xgbParam1, dxTrn, nrounds = 1000, xgbWatchlist, early_stopping_rounds
= 10, eta=0.01, max_depth=6, subsample=0.7, colsample_bytree=0.5 )
# Best iteration [3]:
#	train-auc:0.687282	train-error:0.138171	eval-auc:0.676830	eval-error:0.137100

xgbParamGrid <- expand.grid(max_depth = c(2, 5), eta = c(0.001, 0.01, 0.1) )


```
Lasso Regression (glm)
```{r}
xD<-dfTrn %>% select(-loan_status, -actualTerm, -annRet, -actualReturn, -total_pymnt)
yD<-dfTrn$actualReturn

glmDefault_cv<- cv.glmnet(data.matrix(xD), dfTrn$loan_status, family="binomial")
predDefSc <- predict(glmDefault_cv, data.matrix(dfTst %>% select(-loan_status, -actualTerm, -annRet, -actualReturn, -total_pymnt)), s="lambda.1se", type="class")
glmDefault_cv$lambda.min # 0.000102728
glmDefault_cv$lambda.1se # 0.00615838
tidy(coef(glmDefault_cv, s = glmDefault_cv$lambda.1se))
plot(glmDefault_cv)
plot(glmDefault_cv$glmnet.fit, xvar="lambda")
plot(glmDefault_cv$glmnet.fit)
summary(glmDefault_cv)
```
Elastic-Net Regression (glm)
```{r}
glmls_cv_a2<- cv.glmnet(data.matrix(xDTrn), dfTrn$loan_status, family="binomial", alpha=0.2)
plot(glmls_cv_a2)
glmls_a5<- glmnet(data.matrix(xDTrn), dfTrn$loan_status, family="binomial", alpha=0.5)
plot(glmls_a5)
```
Ridge Regression (glm)
```{r}
yTrn<-factor(if_else(dfTrn$loan_status=="Fully Paid", '1', '0') )
xDTrn<-dfTrn%>% select(-loan_status, -actualTerm, -annRet, -actualReturn, -total_pymnt, -issue_d)
glmls_cv_a0<- cv.glmnet(data.matrix(xDTrn), dfTrn$loan_status, family="binomial", alpha=0)
plot(glmls_cv_a0)
```
Random Forest
```{r}
rfm <- ranger(actualReturn ~., data=subset(dfTrn, select=-c(annRet, actualTerm, loan_status)), num.trees =200, importance='permutation')
rfPredRet_trn<- predict(rfm, dfTrn)
sqrt(mean( (rfPredRet_trn$predictions - dfTrn$actualReturn)^2))
#sqrt(mean( ( (predict(rfm, dfTst))$predictions - dfTst$actualReturn)^2))
plot ( (predict(rfm, dfTst))$predictions, dfTst$actualReturn)
plot ( (predict(rfm, dfTrn))$predictions, dfTrn$actualReturn)
```
Q3
```{r}
xpredTst<-predict(xgb_lsM1, dxTst)
scoreTst_xgb_ls <- dfTst %>% select(grade, loan_status, actualReturn, actualTerm, int_rate) %>% mutate(score=xpredTst)
scoreTst_xgb_ls <- scoreTst_xgb_ls %>% mutate(tile=ntile(-score, 10))
scoreTst_xgb_ls %>% group_by(tile) %>% summarise(count=n(), avgSc=mean(score), numDefaults=sum(loan_status=="Charged Off"), 
avgActRet=mean(actualReturn), minRet=min(actualReturn), maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), 
totB=sum(grade=="B" ), totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )
```
Decile Performance
```{r}
#Performance by deciles
predRet_Trn <- dfTrn %>% select(grade, loan_status, actualReturn, actualTerm, int_rate) %>% mutate(predRet=(predict(rfModel_Ret, dfTrn))$predictions)
predRet_Trn <- predRet_Trn %>% mutate(tile=ntile(-predRet, 10))
predRet_Trn %>% group_by(tile) %>% summarise(count=n(), avgpredRet=mean(predRet), numDefaults=sum(loan_status=="Charged Off"), 
avgActRet=mean(actualReturn), minRet=min(actualReturn), maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), totB=sum(grade=="B" ), totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )
```
Loan status 
```{r}
#Predict loan status
xpredTst<-predict(xgb_lsM1, dxTst)
scoreTst_xgb_ls <- dfTst %>% select(grade, loan_status, actualReturn, actualTerm, int_rate) %>% mutate(score=xpredTst)
scoreTst_xgb_ls <- scoreTst_xgb_ls %>% mutate(tile=ntile(-score, 10))
scoreTst_xgb_ls %>% group_by(tile) %>% summarise(count=n(), avgSc=mean(score), numDefaults=sum(loan_status=="Charged Off"), 
avgActRet=mean(actualReturn), minRet=min(actualReturn), maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), 
totB=sum(grade=="B" ), totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )

#test for above
#codf1 <- subset(codfTst,select=-c(annRet, actualTerm, total_pymnt, actualReturn))
predXgbRet_Tst <- dfTst %>% select(grade, loan_status, actualReturn, actualTerm, int_rate) %>% mutate( predXgbRet=predict(xgb_lsM1, subset(codfTst,select=-c(annRet, actualTerm, total_pymnt, actualReturn))) )
predXgbRet_Tst <- predXgbRet_Tst %>% mutate(tile=ntile(-predXgbRet, 10))
predXgbRet_Tst %>% group_by(tile) %>% summarise(count=n(), avgPredRet=mean(predXgbRet), 
numDefaults=sum(loan_status=="Charged Off"), avgActRet=mean(actualReturn), minRet=min(actualReturn), 
maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), totB=sum(grade=="B" ), 
totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )

#Consider top d deciles from M2, ranked by M1 scores
pRetSc <- predXgbRet_Tst %>% mutate(poScore=scoreTst_xgb_ls$score)
pRet_d <- pRetSc %>% filter(tile<=d)
pRet_d<- pRet_d %>% mutate(tile2=ntile(-poScore, 20))
pRet_d %>% group_by(tile2) %>% summarise(count=n(), avgPredRet=mean(predXgbRet), 
numDefaults=sum(loan_status=="Charged Off"), avgActRet=mean(actualReturn), minRet=min(actualReturn), 
maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), totB=sum(grade=="B" ),
totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )

#considering top d decile from M2
pRet_d<- pRet_d %>% mutate(expRet=predXgbRet*poScore)
pRet_d<- pRet_d %>% mutate(tile2=ntile(-expRet, 20))
pRet_d %>% group_by(tile2) %>% summarise(count=n(), avgPredRet=mean(predXgbRet), 
numDefaults=sum(loan_status=="Charged Off"), avgActRet=mean(actualReturn), minRet=min(actualReturn), 
maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), totB=sum(grade=="B" ), 
totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )

#Modeling loan_statuson lower grade loans - rf (ranger)

lg_dfTst<-dfTst %>% filter(grade=='C'| grade=='D'| grade== 'E'| grade== 'F'| grade== 'G')
rf_M1_lg <- ranger(loan_status ~., data=subset(lg_dfTrn, select=-c(annRet, actualTerm, actualReturn)), num.trees =200, 
probability=TRUE, importance='permutation') 
lg_scoreTstRF <- lg_dfTst %>% select(grade, loan_status, actualReturn, actualTerm, int_rate) %>% 
mutate(score=(predict(rf_M1_lg,lg_dfTst))$predictions[,"Fully Paid"])
lg_scoreTstRF <- lg_scoreTstRF %>% mutate(tile=ntile(-score, 10))
lg_scoreTstRF %>% group_by(tile) %>% summarise(count=n(), avgSc=mean(score), numDefaults=sum(loan_status=="Charged Off"), avgActRet=mean(actualReturn), minRet=min(actualReturn), 
maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), totB=sum(grade=="B" ), 
totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F"))
```
ntile for glmnet
```{r}
predRet_Trn <- predRet_Trn %>% mutate(tile=ntile(-predRet, 10))
predRet_Trn %>% group_by(tile) %>% summarise(count=n(), avgpredRet=mean(predRet), numDefaults=sum(loan_status=="Charged Off"), 
avgActRet=mean(actualReturn), minRet=min(actualReturn), maxRet=max(actualReturn), avgTer=mean(actualTerm), totA=sum(grade=="A"), 
totB=sum(grade=="B" ), totC=sum(grade=="C"), totD=sum(grade=="D"), totE=sum(grade=="E"), totF=sum(grade=="F") )

```
